---
title: 'Lab: R Bootcamp'
output: html_document
---

As you have seen in lecture, we’ll be using RMarkdown files almost exclusively. There are several options when creating a new file in RStudio, but I find that RMarkdown files are the best when starting out. One of the reasons being that you can have both nice-looking text (regular, markdown, latex) and code in the same document. This is especially convenient for collaborating with others and making your work as reproducible as possible.

Let's get more comfortable writing R code and documenting our results by using the `murders` dataset from `dslabs`. Be sure to include text answers where appropriate. 

```{r}
library(dslabs)
data(murders)
```


1. Compute the per 100,000 murder rate for each state and store it in an object called `murder_rate`. Then use the logical operators to create a logical vector named `low` that tells us which entries of `murder_rate` are lower than 1. 

```{r}
# Your code here
```


2. Now use the results from the previous exercise and the function `which` to determine the indices of `murder_rate` associated with values lower than 1.

```{r}
# Your code here
```

3. Use the results from the previous exercise to report the names of the states with murder rates lower than 1.

```{r}
# Your code here
```


4. Now extend the code from exercises 2 and 3 to report the states in the Northeast with murder rates lower than 1. Hint: Use the previously defined logical vector `low` and the logical operator `&`.

```{r}
# Your code here
```

5. Use the `%in%` operator to create a logical vector that answers the question: which of the following are actual abbreviations: MA, ME, MI, MO, MU?

```{r}
# Your code here
```

6. The function `nchar` tells you how many characters long a character vector is. For example:
    
```{r}
char_len <- nchar(murders$state)
char_len[1:5]
```


Write a line of code that assigns to the object `new_names` the state abbreviation when the state name is longer than 8 characters.

```{r}
# Your code here
```